RSA_model2

### 2015-10-30 analysis/e10_analysis.Rmd
getting rid of delted files

```{r}

rm(list=ls())
setwd("~/Desktop/Projects/scalar_implicature/")
source("analysis/useful_dplyr.R")
library(tidyr)
library(dplyr)
library("rjson")

@@

Holding off on exclusions (but exclusion code here)
---------------------------------------------------
```{r}
d <- d.raw %>% filter(scale != "training1")
# compliant <- d.raw %>% 
#   filter(grepl("training", scale)) %>%
#   group_by(workerid) %>%
#   summarise(compliant = judgment[scale == "training1" & degree == "hi"] > 3 & 
#               judgment[scale == "training1" & degree == "low"] < 3)
#   
# d <- d.raw %>% 
#   left_join(compliant) %>%
#   filter(grepl(pattern = "english", 
#                language, ignore.case = TRUE), 
#          domain != "training1", 
#          domain != "training2", 
#          compliant == TRUE)
```

@@

Let's remove training runs
```{r}
d.raw = d.raw[c(-1, -2), ]       # remove first two rows
d = d.raw %>% filter(scale != "training1")
```

@@

>>>>

```{r}
rm(list=ls())
setwd("~/Desktop/Projects/scalar_implicature/")
source("analysis/useful_dplyr.R")
library(tidyr)
library(dplyr)
library("rjson")

@@

Exclusions (but exclusion code here)
---------------------------------------------------
```{r}
compliant <- d.raw %>% 
  filter(grepl("training", scale)) %>%
  group_by(workerid) %>%
  summarise(compliant = (judgment[scale == "training1" & degree == "hi2"] == 1) && 
              (judgment[scale == "training1" & degree == "low1"] == 1))

num_uncompliant = sum(compliant$compliant == FALSE)
num_uncompliant

d <- d.raw %>% 
  left_join(compliant) %>%
  filter(grepl(pattern = "english", 
               language, ignore.case = TRUE), 
         scale != "training1",  
         compliant == TRUE)
d <- d.raw %>% filter(scale != "training1")

# new sample after filtering compliant and English
length(unique(d$workerid))
head(d)
```

@@

Let's remove training runs
```{r}
#d.raw = d.raw[c(-1, -2), ]       # remove first two rows
#d = d.raw %>% filter(scale != "training1")
```

@@

Write to csv
```{r}
write.csv(ms, "models/e10.csv", row.names=FALSE)
```

### 2015-10-30 analysis/e5_analysis2.Rmd
getting rid of delted files

Preliminaries.

```{r}

@@

Read in files and consolidate to the same directory.

```{r}
files <- dir("production-results/e5/", pattern = "*.json")
d.raw <- data.frame()

@@

Holding off on exclusions - everyone put English, and training 2 was confusing. 
```{r}
# compliant <- d.raw %>% 
#   filter(grepl("training", scale)) %>%
#   group_by(workerid) %>%
#   summarise(compliant = judgment[scale == "training1" & degree == "hi"] > 3 & 
#               judgment[scale == "training1" & degree == "low"] < 3)
#   
# d <- d.raw %>% 
#   left_join(compliant) %>%
#   filter(grepl(pattern = "english", 
#                language, ignore.case = TRUE), 
#          domain != "training1", 
#          domain != "training2", 
#          compliant == TRUE)
d <- d.raw %>% filter(scale != "training1")
```

Main Analysis
-------------
```{r}
names(d)
dim(d)
# removing language - main data.frame()
d$stars = as.numeric(as.character(d$stars))/20
dt = d[, -6]
scalars = c("some_all", "liked_loved", "palatable_delicious",
            "good_excellent", "memorable_unforgettable")
dgrs = c("low", "hi")
```

Histogram Plots for our scalars
```{r}
scalar.agreements = function(scalar_pair, degree) {
  pair = dt[which(dt$scale == scalar_pair), ]
  scalar = pair[which(pair$degree == degree), ]
  scalar = spread(scalar, stars, judgment)
  # plots
  par(mfrow = c(2,3))
  wrd = unlist(strsplit(scalar_pair, "_"))
  wrd = ifelse(degree == "low", wrd[1], wrd[2])
  likert.plots(scalar, wrd)
}
likert.plots = function(scalar, wrd) {
  barplot( table(scalar$"1"), main = paste(wrd, ": *"),
           xlab="Agree", ylab="Counts")
  barplot( table(scalar$"2"), main = paste(wrd, ": **"),
           xlab="Agree", ylab="Counts")
  barplot( table(scalar$"3"), main = paste(wrd, ": ***"),
           xlab="Agree", ylab="Counts")
  barplot( table(scalar$"4"), main = paste(wrd, ": ****"),
           xlab="Agree", ylab="Counts")
  barplot( table(scalar$"5"), main = paste(wrd, ": *****"),
           xlab="Agree", ylab="Counts")
}
for (i in scalars) {
  for (j in dgrs) {
    scalar.agreements(i, j)
  }
}
```

Matching in data
```{r}
match = dt$stars == dt$judgment
par(mfrow=c(1,1))
barplot(c("T" = mean(match), "F" = (1 - mean(match))), main = "Percent matches (judgements and stars")
dm = data.frame(dt, match)

@@

Rolling 1,2 4,5
```{r}
ds = d[, -6] %>%
  group_by(scale, degree, stars) %>%
  summarise(speaker.hi = sum( ifelse( (judgment > 3), 1, 0)),
            speaker.mid = sum( ifelse( (judgment == 3), 1, 0)),
            speaker.lo = sum( ifelse( (judgment < 3), 1, 0)))

>>>>

Workspace
---------
```{r}

@@

Data prep
---------
```{r}
files <- dir("production-results/e5/", pattern = "*.json")
d.raw <- data.frame()

@@

Holding off on exclusions (but exclusion code here)
---------------------------------------------------
```{r}
d <- d.raw %>% filter(scale != "training1")
# compliant <- d.raw %>% 
#   filter(grepl("training", scale)) %>%
#   group_by(workerid) %>%
#   summarise(compliant = judgment[scale == "training1" & degree == "hi"] > 3 & 
#               judgment[scale == "training1" & degree == "low"] < 3)
#   
# d <- d.raw %>% 
#   left_join(compliant) %>%
#   filter(grepl(pattern = "english", 
#                language, ignore.case = TRUE), 
#          domain != "training1", 
#          domain != "training2", 
#          compliant == TRUE)
```

Main analysis below
-------------------
```{r}
names(d)
dim(d)
# removing language - main data.frame()
d$stars = as.numeric(as.character(d$stars))/20
dt = d[, -6]
scalars = c("some_all", "liked_loved", "palatable_delicious",
            "good_excellent", "memorable_unforgettable")
dgrs = c("low", "hi")
```

Histogram Plots for our scalars
-------------------------------
```{r}
scalar.agreements = function(scalar_pair, degree) {
  pair = dt[which(dt$scale == scalar_pair), ]
  scalar = pair[which(pair$degree == degree), ]
  scalar = spread(scalar, stars, judgment)
  # plots
  par(mfrow = c(2,3))
  wrd = unlist(strsplit(scalar_pair, "_"))
  wrd = ifelse(degree == "low", wrd[1], wrd[2])
  likert.plots(scalar, wrd)
}
likert.plots = function(scalar, wrd) {
  barplot( table(scalar$"1"), main = paste(wrd, ": *"),
           xlab="Agree", ylab="Counts")
  barplot( table(scalar$"2"), main = paste(wrd, ": **"),
           xlab="Agree", ylab="Counts")
  barplot( table(scalar$"3"), main = paste(wrd, ": ***"),
           xlab="Agree", ylab="Counts")
  barplot( table(scalar$"4"), main = paste(wrd, ": ****"),
           xlab="Agree", ylab="Counts")
  barplot( table(scalar$"5"), main = paste(wrd, ": *****"),
           xlab="Agree", ylab="Counts")
}

# plotting all scalars --> for pdf print out, not working
for (i in scalars) {
  for (j in dgrs) {
    scalar.agreements(i, j)
  }
}

# call to plot single scalar
scalar.agreements("palatable_delicious", "hi")

lm.overall = lm(judgment~stars + degree + scale, data=dt)
summary(lm.fit)
cor(dt$judgment, dt$stars)

# Overall matching
par(mfrow=c(1,1))
plot(jitter(dt$stars), jitter(dt$judgment),
     main = "Matching between stars and judgments", xlab = "Judgment", ylab = "Stars")
abline(lm(judgment~stars, data=dt), col="green")

# Low and High matching
low.obs = which(dt$degree == "low")
hi.obs = -low.obs
par(mfrow=c(1,2))
plot(jitter(dt[low.obs, ]$stars), jitter(dt[low.obs, ]$judgment),
     main = "Low Degree", xlab = "Judgment", ylab = "Stars")
abline(lm(judgment~stars, data=dt[low.obs,]), col="red")

plot(jitter(dt[hi.obs, ]$stars), jitter(dt[hi.obs, ]$judgment),
     main = "High Degree", xlab = "Judgment", ylab = "Stars")
abline(lm(judgment~stars, data=dt[hi.obs,]), col="blue")
```

Matching in data
----------------
```{r}
match = dt$stars == dt$judgment
par(mfrow=c(1,1))
barplot(c("T" = mean(match), "F" = (1 - mean(match))), main = "Percent matches (judgements and stars")
dm = data.frame(dt, match)

@@

# Rolling [1,2] [4,5]
---------------------
```{r}
ds = d[, -6] %>%
  group_by(scale, degree, stars) %>%
  summarise(speaker.hi = sum( ifelse( (judgment > 3), 1, 0)),
            speaker.mid = sum( ifelse( (judgment == 3), 1, 0)),
            speaker.lo = sum( ifelse( (judgment < 3), 1, 0)))

### 2015-10-30 analysis/e9_altsAnalysis.Rmd
getting rid of delted files

**Output to text file for reference:**
```{r}
d.topTen =  d.topTen[order(d.topTen$scale, -d.topTen$n),]
write.table(d.topTen, "analysis/top_alts_output.txt")
```

>>>>

**Output top ten to text file for reference:**
```{r}
d.topTen =  d.topTen[order(d.topTen$scale, -d.topTen$n),]
write.table(d.topTen, "analysis/top_alts_output.txt")
```

### 2015-10-30 models/Model_Playspace.Rmd
getting rid of delted files

```{r}
# Priors ---------------->
emp.priors = read.csv("models/prior.csv")
yelp.priors = read.csv("models/yelp1_priors.csv")
priors = yelp.priors
# Possible transformations --->
#priors$prior.p = sqrt(priors$prior.p)/(sum(sqrt(priors$prior.p)))
#priors$prior.p = (1/(-log(priors$prior.p))) / sum((1/(-log(priors$prior.p))))
#priors$prior.p = (log(priors$prior.p + 1)) / sum((log(priors$prior.p + 1)))

# Speaker informativity ------------------------->
speaker = read.csv("models/speaker.csv")
speaker = read.csv("models/speaker_normed.csv") # for printing out semantic distr's
speaker = read.csv("models/yelp1.csv")
#speaker = read.csv("models/e5a.csv")

@@

# non-normalized posterior 
# ------------------------
nn.post = function(rating, degree, m, alpha, useprior) {

  if (useprior) {
    prior <- priors[rating, "prior.p"]
  } else { #unif prior
    prior = .2 
  }
  speaker.prob(rating, degree, m, alpha) * prior
}

@@

```{r}
# data
# ----
data <- left_join(speaker, listener) %>%
  left_join(emp.priors) %>%
  rowwise %>%
  select(scale, degree, stars, speaker.p, listener.p, prior.p) %>%
  mutate(listener.p = ifelse(is.na(listener.p), 0, listener.p)) %>%
  group_by(scale)
```

@@

# Which alpha has tightest correlation with human judgements
alphas = seq(from=1, to=20)
fit = sapply(alphas, FUN=function(n) {
  md <- data %>%
    do(run.rsa(., alpha = n, useprior = T, usenone = TRUE))

@@

# RUN MODEL
# ---------
md <- data %>%
  do(run.rsa(., alpha = best.alpha, useprior = T, usenone = TRUE))
```

>>>>

```{r}
# Priors ---------------->
emp.priors = read.csv("models/prior.csv")
yelp.priors = read.csv("models/yelp1_priors.csv")
priors = data.frame(stars=seq(1,5), prior.p=rep(0.2,5))
# Possible transformations --->
#priors$prior.p = sqrt(priors$prior.p)/(sum(sqrt(priors$prior.p)))
#priors$prior.p = (1/(-log(priors$prior.p))) / sum((1/(-log(priors$prior.p))))
#priors$prior.p = (log(priors$prior.p + 1)) / sum((log(priors$prior.p + 1)))

# Speaker informativity ------------------------->
speaker = read.csv("models/e8.csv")
#speaker = read.csv("models/speaker_normed.csv") # for printing out semantic distr's
#speaker = read.csv("models/yelp1.csv")
#speaker = read.csv("models/e5a.csv")

@@

# non-normalized posterior 
# ------------------------
nn.post = function(rating, degree, m, alpha, useprior) {
  if (useprior) {
    prior <- priors[rating, "prior.p"]
  } else { #unif prior
    prior = .2 
  }
  speaker.prob(rating, degree, m, alpha) * prior
}

@@

```{r}
# data
# ----
data <- left_join(speaker, listener) %>%
  left_join(emp.priors) %>%
  rowwise %>%
  select(scale, degree, stars, speaker.p, listener.p, prior.p) %>%
  mutate(listener.p = ifelse(is.na(listener.p), 0, listener.p)) %>%
  group_by(scale)
tail(data)
```

@@

# Which alpha has tightest correlation with human judgements
alphas = seq(from=1, to=20)
fit = sapply(alphas, FUN=function(n) {
  md <- data %>%
    do.call(run.rsa(., alpha = n, useprior = T, usenone = TRUE))

@@

# RUN MODEL
# ---------
md <- data %>%
  do(run.rsa(., alpha = 1, useprior = T, usenone = F))
```

### 2015-10-30 models/RSA_Model2.Rmd
getting rid of delted files

library(knitr)
library(rjson)
library(dplyr)
library(tidyr)

opts_chunk$set(cache=TRUE)
setwd("~/Desktop/Projects/scalar_implicature/")
source("analysis/useful_dplyr.R")
```

Data
----
```{r}
speaker = read.csv("models/e8.csv")
listener = read.csv("models/listener.csv")
# priors
# ------
unif = data.frame(stars = seq(1, 5), prior.p = rep(0.2, 5))
empirical = read.csv("models/prior.csv")
yelp = read.csv("models/yelp1_priors.csv")
priors = unif
# combine speaker / listener
data <- left_join(speaker, listener) %>%
  left_join(priors) %>%
  rowwise %>%
  select(scale, degree, stars, speaker.p, listener.p, prior.p) %>%
  mutate(listener.p = ifelse(is.na(listener.p), 0, listener.p)) %>%
  group_by(scale)
head(data)
```

>>>>

library(ggplot2)
library(knitr)
library(rjson)
library(dplyr)
library(tidyr)

#setwd("~/Desktop/Projects/scalar_implicature/")
#source("analysis/useful_dplyr.R")
```

Data
----
```{r}
speaker = read.csv("~/Desktop/Projects/scalar_implicature/models/e8.csv")
listener = read.csv("~/Desktop/Projects/scalar_implicature/models/listener.csv")
# priors
# ------
unif = data.frame(stars = seq(1, 5), prior.p = rep(0.2, 5))
empirical = read.csv("~/Desktop/Projects/scalar_implicature//models/prior.csv")
yelp = read.csv("~/Desktop/Projects/scalar_implicature//models/yelp1_priors.csv")
priors = unif
# combine speaker / listener
data <- left_join(speaker, listener) %>%
  left_join(priors) %>%
  rowwise %>%
  select(scale, degree, stars, speaker.p, listener.p, prior.p) %>%
  mutate(listener.p = ifelse(is.na(listener.p), 0, listener.p)) %>%
  group_by(scale)
head(data)
```
